---
title: "Exporting"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Exporting}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)
```

```{r setup, include=FALSE, echo=FALSE}
library(susoapi)
```

# User interface

In Survey Solutions's user interface, exporting involves a few sequential steps:

- Select a template
- Select a version of that template
- Specify the status of interviews to export (default: all)
- Select:
  - Data type: microdata or paradata
  - Whether to include questionnaire paradata
  - Data export format: tab-separated, Stata, or SPSS
- Click on `ADD TO QUEUE`
- Cick on `DOWNLOAD` when the export files are available

# API

Via the API, the steps are similar but different:

- Submit an export job
- Check whether the job is complete
- Download the file when the job is complete

# `susoapi`

With `susoapi`, this translates to the following sequence of function calls.

First, start an export job, by specifying all of the particulars:

```{r start_job}
# set server authentication credentials
set_credentials(
  server = "https://exampleserver.com",
  workspace = "myworkspace",
  user = "My_API_user10",
  password = "MySecretPassword2Day123"
)

# start an export job
# specifying same same options as in user interface
# optionally specifying other options--including some not available in the UI
start_export(
  qnr_id = "72f7160c-12dc-4dd4-9df1-66af819e434d$1",
  export_type = "STATA",
  interview_status = "All",
  include_meta = TRUE
) -> started_job_id
```

Then, check on the job's status:

```{r check_job}
# check export job progess,
# specifying ID of job started in prior step
get_export_job_details(job_id = started_job_id)
```

Repeat job status queries until the job is complete.

Next, download the file produced by the completed job:

```{r download_file}
# download the export file, 
# specifying:
# - job ID
# - where to download the file
get_export_file(
    job_id = started_job_id,
    path = "C:/your/file/path/"
)
```

Alternatively, see [`susoflows`](https://github.com/arthur-shaw/susoflows) for functions that automate this and similar export worflows.
