---
title: "Introduction to susoapi"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to susoapi}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)
```

```{r setup, include = FALSE, echo=FALSE}
library(susoapi)
```

# Overview

The `susoapi` package aims to provide an R wrapper function for each Survey Solutions API endpoint, and in so doing enable users to take all API actions without leaving R.

# Set credentials

Before any of these functions can be used, the user must set their credentails to be authenticated by the server.

While authentication could be provided separately for each function call as part of its arguments, it is better and more efficient to use the `set_credentials()` function to capture the credentials and make them available to all function calls. For example:

```{r set_credentials}
# first, set credentials for connecting with the server
set_credentials(
  server = "https://example.server",
  user = "My_API_user1",
  password = "MySecretPassword2Day"
)

# then, get all questionnaires
# the arguments of this function are: server, user, and password
# but they are provided to the function by the values stored by `set_credentials()`
get_questionnaires()

```

# Take actions

To take an individual action, one simply needs to find the appropriate function. The reference arranges functions according to their area:

- Questionnaires
- Assignments
- Interviews
- Users
- Export

For example, to gather all questionnaires loaded on the server:

```{r get_questionnaires}
# collect all questionnaires and data about them,
# using previously set server credentials
get_questionnaires()
```

# Chain actions

To take a series of related actions, users have two choices:

1. Chain commands explicitly
2. Use other tools that do this implicitly

## Examples of explicitly chained commands

### Export data

To export data, one needs to make a sequence of function calls.

First, start an export job, by specifying all of the particulars:

```{r start_job}
# set server authentication credentials
set_credentials(
  server = "https://exampleserver.com",
  user = "My_API_user10",
  password = "MySecretPassword2Day123"
)

# start an export job
# specifying same same options as in user interface
# optionally specifying other options--including some not available in the UI
start_export(
  qnr_id = "72f7160c-12dc-4dd4-9df1-66af819e434d$1",
  export_type = "STATA",
  interview_status = "All",
  include_meta = TRUE
) -> started_job_id
```

Then, check on the job's status:

```{r check_job}
# check export job progess,
# specifying ID of job started in prior step
get_export_job_details(job_id = started_job_id)
```

Repeat job status queries until the job is complete.

Next, download the file produced by the completed job:

```{r download_file}
# download the export file, 
# specifying:
# - job ID
# - where to download the file
get_export_file(
    job_id = started_job_id,
    path = "C:/your/file/path/"
)
```

### Monitor user

To monitor user activity on tablets, one needs to follow these steps.

First, collect the list of users and their profile details

```{r get_users}
# collect all interviewers, their supervisors, and their attributes
# this includes both account details and personal details
all_users <- get_interviewers()
```

Then, identify the user of interest by filtering the data.

```{r filter_users}
library(dplyr)

# extract the user ID for the target user
# this will be used as a parameter for the next step
target_user_id <- filter(all_users, UserName == "TestInt007") %>%
  pull(UserId)

```

Next, request the action log of all tablet activity for the target user.

```{r, get_tablet_activity}
# collect a log of activity on the tablet within specified dates
tablet_activity <- get_user_action_log(
  user_id = target_user_id,
  start = "2020-02-15",
  end = "2020-03-15"
)
```

## Other tools

Alternatively, for certain tasks, users can rely on [`susoflows`](https://github.com/arthur-shaw/susoflows), a package that aims to wrap common workflows in single functions (e.g., download data).
